Rank verification for exponential families

### 2016-04-05 verifying-winner.tex
Expanded paragraph on power comparison

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$.}
\label{fig:power}
\end{figure}

>>>>

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth, trim = {1.3in 0.7in 1.6in 0.6in}, clip]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$. The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
\label{fig:power}
\end{figure}
